---
title: "Survival Analysis HW4"
author: "Zhuodiao Kuang"
date: "`r Sys.Date()`"
output: html_document
---

# Problem 1

### a) Construct the 17 2x2 tables for the log-rank test.

|i|Group|Events at $t_{(i)}$|Survival at $t_{(i)}^+$|Expected|At risk at $t_{(i)}^-$|
|---|---|---|---|---|---|
|1|0|0|21|1|21|
|-|1|2|19|1|21|
|-|-|2|40|-|42|
|---|---|---|---|---|---|
|2|0|0|21|1.05|21|
|-|1|2|17|0.95|19|
|-|-|2|38|-|40|
|---|---|---|---|---|---|
|3|0|0|21|0.55|21|
|-|1|1|16|0.45|17|
|-|-|1|37|-|38|
|---|---|---|---|---|---|
|4|0|0|21|1.14|21|
|-|1|2|14|0.86|16|
|-|-|2|35|-|37|
|---|---|---|---|---|---|
|5|0|0|21|1.2|21|
|-|1|2|12|0.8|14|
|-|-|2|33|-|35|
|---|---|---|---|---|---|
|6|0|3|18|1.91|21|
|-|1|0|12|1.09|12|
|-|-|3|30|-|33|
|---|---|---|---|---|---|
|7|0|1|16|0.59|17|
|-|1|0|12|0.41|12|
|-|-|1|28|-|29|
|---|---|---|---|---|---|
|8|0|0|16|2.29|16|
|-|1|4|8|1.71|12|
|-|-|4|24|-|28|
|---|---|---|---|---|---|
|10|0|1|14|0.65|15|
|-|1|0|8|0.35|8|
|-|-|1|22|-|27|
|---|---|---|---|---|---|
|11|0|0|13|1.24|13|
|-|1|2|6|0.76|8|
|-|-|2|19|-|21|
|---|---|---|---|---|---|
|12|0|0|12|1.33|12|
|-|1|2|4|0.67|6|
|-|-|2|16|-|18|
|---|---|---|---|---|---|
|13|0|1|11|0.75|12|
|-|1|0|4|0.25|4|
|-|-|1|15|-|16|
|---|---|---|---|---|---|
|15|0|0|11|0.73|11|
|-|1|1|3|0.27|4|
|-|-|1|14|-|15|
|---|---|---|---|---|---|
|16|0|1|10|0.79|11|
|-|1|0|3|0.21|3|
|-|-|1|13|-|14|
|---|---|---|---|---|---|
|17|0|0|10|0.77|10|
|-|1|1|2|0.23|3|
|-|-|1|12|-|13|
|---|---|---|---|---|---|
|22|0|1|6|1.56|7|
|-|1|1|1|0.44|2|
|-|-|2|7|-|9|
|---|---|---|---|---|---|
|23|0|1|5|1.71|6|
|-|1|1|0|0.29|1|
|-|-|2|5|-|7|
|---|---|---|---|---|---|


### b) Verify the rank statistics by calculating the difference of the observed and expected in each 2x2 tables

```{r}
d0_e0<-c(0-1,0-1.05,0-0.55,0-1.14,0-1.2,3-1.91,1-0.59,
         0-2.29,1-0.65,0-1.24,0-1.33,1-0.75,0-0.73,1-0.79,0-0.77,1-1.56,1-1.71)



```

The series is `r d0_e0`. The sum of each difference of the observed and expected is `r sum(d0_e0)`. The calculation result differs slightly from the actual result due to the retention of decimals.

The result is same as the following rank statistics:

$$L= \sum_{i=1}^k(d_{0i}-e_{0i})=-10.25$$


### c) Include the variance calculation for each of the 2x2 tables as well and verify that

$$var(L) = \sum_{i=1}^k \frac{n_{0i}n_{1i}d_i(n_i-d_i)}{n_i^2(n_i-1)}=6.26$$

```{r}
n0 <- c(21,21,21,21,21,21,17,16,15,13,12,12,11,11,10,7,6)
n1 <- c(21,19,17,16,14,12,12,12,8,8,6,4,4,3,3,2,1) 
n <- c(42,40,38,37,35,33,29,28,23,21,18,16,15,14,13,9,7)
d <- c(2,2,1,2,2,3,1,4,1,2,2,1,1,1,1,2,2)

L=sum(n0*n1*d*(n-d)/(n^2*(n-1)))
L
```



